中国营商环境的地区差异、时空演变与收敛性研究

### 2021-04-26 paper.Rmd
new

\begin{equation}
f(x) = \frac{1}{\sqrt{2\pi}Nh_N}\sum_{i = 1}^{N}\frac{e^{-\frac{1}{2}(\frac{X_{i}-x}{\lambda_ih_N})^2}}{\lambda_i} \tag{14}
\end{equation}

@@

@@

final_index_tweak %>% 
  dplyr::filter(year == 2019) %>% 
  group_sort(location,province,index) %>% 
  ggplot(aes(province,index,fill = location))+
  geom_col()+coord_flip()+
  labs(x = "",y = "得分",fill = "地区")+
  # scale_fill_manual(values = c("black","blue","green"))+
  scale_color_viridis_d()+
  scale_y_continuous(limits = c(0,1.25))+
  theme(
    text = element_text(family = cnfont),
    plot.margin = margin(20,20,20,20),
    legend.position = "bottom",
    axis.text.y.left = element_text(size = 8)
  )

>>>>

\begin{equation}
f(x) = \frac{1}{\sqrt{2\pi}Nh_N}\sum_{i = 1}^{N}\frac{e^{-\frac{1}{2}(\frac{X_i}{\lambda_ih_N})^2}}{\lambda_i} \tag{14}
\end{equation}

@@

```{r echo=FALSE}
load("final_index.rda")
load("raw.rda")
pacman::p_load(lubridate,sf,geojsonsf,geojsonio,jsonlite,haven)

final_index %>%  
  mutate(index = (index -min(index))/(max(index)-min(index))) %>% 
  mutate(new = round(index,3)) -> final_index

prov_unify <- function(df,province=province) {
  df %>% pull({{province}}) -> target
  if_else(str_detect(target,"[内蒙古黑龙]"),
          str_replace_all(target,"(.{3}).*","\\1"),
          str_replace_all(target,"(.{2}).*","\\1")) -> target
  df %>% bind_cols(target) %>% rename("new" = ncol(.)) %>%
    relocate(ncol(.),.after = {{province}}) %>% select(-{{province}}) %>%
    rename("province" = "new")
} # end of "cn_province"

raw %>% prov_unify(省) %>% 
  sf_geojson() %>% 
  fromJSON(simplifyVector = FALSE) -> provmap

final_index %>% dplyr::filter(year == 2019) %>% pull(4) %>% quantile() -> qqq

highchart() %>% # 使用JavaScript方式
  hc_chart(
    type = "map", # 指定何种geoms
    spacingBottom = 10,
    spacingTop = 10,
    spacingLeft = 10,
    spacingRight = 10,
    style = list(
      fontFamily = cnfont
    )
  ) %>% 
  hc_add_series_map(map = provmap,
                    df = final_index %>% dplyr::filter(year == 2019), 
                    joinBy = c("province", "province"), 
                    value = "index", 
                    name = "营商环境指标：",
                    borderWidth = 1,
                    borderColor = "white",
                    states = list(hover = list(color = '#bada55')),
                    dataLabels = list(enabled = FALSE)) %>% 
  hc_add_series(
    data = provmap,
    type = "mapline",geojson = T,
    color = "black",borderWidth = 0.5,show.legend = T
  ) %>% 
  hc_colorAxis(dataClasses = list(
    list(to = qqq[[1]], color = alpha("grey",0.2), name = "数据缺失"),
    list(from = qqq[[1]], to = qqq[[2]], color = alpha("grey",0.5)),
    list(from = qqq[[2]], to = qqq[[3]], color = alpha("grey",0.8)),
    list(from = qqq[[3]], to = 1.2, color = "grey"))) %>% 
  hc_tooltip(headerFormat = "",
        pointFormat = "<b>{point.province}</b><br>营商环境指标：{point.new}",
             borderRadius = 5) %>% 
  hc_legend(align = 'center',
            # layout = 'horizontial',
            verticalAlign = "bottom",
            itemMarginTop= 3,
            itemMarginBottom= 3,
            valueDecimals = 3,
            # floating = TRUE,
            symbolRadius = 0,
            # x = 200, y = -20,
            symbolHeight = 14, 
            title = list(text = " ")) %>% 
  hc_title(
    text = str_c(2019,"年全国各地营商环境指标分布情况")
  )
```

@@

load("final_index.rda")
final_index %<>% mutate(index = (index-min(index))/(max(index)-min(index)))

final_index %>% 
  dplyr::filter(year == 2019) %>% 
  group_sort(location,province,index) %>% 
  ggplot(aes(province,index,fill = location))+
  geom_col(color = alpha("white",0.5))+coord_flip()+
  # geom_hline(yintercept = qqq[[2]],linetype = "dashed",color = "black")+
  # geom_hline(yintercept = qqq[[3]],linetype = "dashed",color = "black")+
  # geom_hline(yintercept = qqq[[4]],linetype = "dashed",color = "black")+
  labs(x = "",y = "得分",fill = "地区")+
  scale_fill_manual(values = c(alpha("black",0.2),"darkgrey",alpha("black",0.6)))+
  # scale_color_viridis_d()+
  scale_y_continuous(limits = c(0,1.25))+
  theme(
    text = element_text(family = cnfont),
    plot.margin = margin(20,20,20,20),
    legend.position = "bottom",
    axis.text.y.left = element_text(size = 8)
  )
